Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added a figure for number of buildings

\begin{figure}[tb]
	\centering
	\includegraphics{Data}
	\caption{Data.
		There are $2{,}590$ buildings, 
		which have $19{,}255$ edges in total.}
	\label{fig:Data}
\end{figure}

@@

\fig\ref{fig:ExperimentalComparison} shows a comparison of 
our result at time $t=1$
and the data from IGN at scale $1:50{,}000$.
No small buildings are removed in our result or the IGN data.
The boundaries of our built-up areas are more straight than that of IGN data, 
where we have $1{,}135$ edges while the data has $4{,}968$ edges.

@@

>>>>

\begin{figure}[tb]
	\centering
	\includegraphics{Data}
	\caption{Data.
		There are $2{,}590$ buildings, 
		which in total have $19{,}255$ edges and have area
		$448{,}996.8\,\mathrm{mm}^2$.}
	\label{fig:Data}
\end{figure}

%	axis x line=bottom,
%axis y line=left,
\begin{figure}[tb]
	\centering
	\begin{tikzpicture}[]
	\begin{axis}[
	width= \linewidth-0.1cm,
	axis lines = left,
%	axis x line=center,
%	axis y line=left,
	xtick={0.1,0.2,...,1},
	ytick={500,1000,...,3000},
	xlabel={$t$},
	ylabel={number of buildings},
%	xlabel style={below right},
%	ylabel style={above left},
	xmin=0,
	xmax=1.1,
	ymin=0,
	ymax=3200,
	cycle list name=black white,
	]
	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
	\addplot+  coordinates {
		(0,2590)
		(0.1,1963)
		(0.2,758)
		(0.3,304)
		(0.4,177)
		(0.5,122)
		(0.6,92)
		(0.7,73)
		(0.8,66)
		(0.9,59)
		(1,56)		
	};
	\legend{\quad $M=200{,}000$, \quad $M=400{,}000$}
	\end{axis}
	\end{tikzpicture}
	\caption{The numbers of regions where our approach was 
		forced to use the given overestimation factors in order 
		to 
		find a solution without exploring more than $M \in 
		\{200{,}000,~400{,}000\}$ nodes of the subdivision 
		graph.}
	\label{fig:OverestimationStatistics}
\end{figure}

@@

\fig\ref{fig:ExperimentalComparison} shows a comparison of 
our result at time $t=1$
and the data from IGN at scale $1:50{,}000$.
No small buildings are removed in our result or the IGN data.
The boundaries of our built-up areas are more straight than that of IGN data, 
where we have $1{,}135$ edges while the data has $4{,}968$ edges.
From this perspective, we would say that our result is 
more reasonable than the existing data.
A questionnaire, however, is needed to compare our result with the data.

Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{mm}^2$.

@@

We proposed a method to continuously generalize buildings to built-up areas
by aggregating and growing.
Using
